Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2020-12-30 submission/NatCom_cv_models.tex
images updated

\begin{figure}[t]
    \centering
    \subfigure[Log Frobenius Norm, VGG ]{
        \includegraphics[width=4.9cm]{img/VGG_lognorm_accs.png}
        \label{fig:vgg-fnorm}
    }
    \qquad
    \subfigure[Log Spectral Norm, VGG ]{
        \includegraphics[width=4.9cm]{img/VGG_spectralnorm_accs.png}
        \label{fig:vgg-snorm}
    }
    \qquad
    \subfigure[ Weighted Alpha, VGG ]{
        \includegraphics[width=4.9cm]{img/VGG_alpha_weighted_accs.png}
        \label{fig:vgg-walpha}
    }
    \qquad
    \subfigure[Log $\alpha$-Norm, VGG ]{
        \includegraphics[width=4.9cm]{img/VGG_logpnorm_accs.png}
        \label{fig:vgg-pnorm}
    }
    \caption{Comparison of Average Log Norm and Weighted Alpha quality metrics versus reported test accuracy for pretrained VGG models: 
             VGG11, VGG13, VGG16, and VGG19, with and without Batch Normalization (BN),
             trained on ImageNet, available in pyTorch (v1.4).  
             Metrics fit by linear regression, RMSE reported.  }
    \label{fig:vgg-metrics}
\end{figure}

>>>>

\begin{figure}[t]
    \centering
    \subfigure[Log Frobenius Norm, VGG ]{
        \includegraphics[width=4.9cm]{img/VGG_log_norm_accs.png}
        \label{fig:vgg-fnorm}
    }
    \qquad
    \subfigure[Log Spectral Norm, VGG ]{
        \includegraphics[width=4.9cm]{img/VGG_log_spectral_norm_accs.png}
        \label{fig:vgg-snorm}
    }
    \qquad
    \subfigure[ Weighted Alpha, VGG ]{
        \includegraphics[width=4.9cm]{img/VGG_alpha_weighted_accs.png}
        \label{fig:vgg-walpha}
    }
    \qquad
    \subfigure[Log $\alpha$-Norm, VGG ]{
        \includegraphics[width=4.9cm]{img/VGG_log_alpha_norm_accs.png}
        \label{fig:vgg-pnorm}
    }
    \caption{Comparison of Average Log Norm and Weighted Alpha quality metrics versus reported test accuracy for pretrained VGG models: 
             VGG11, VGG13, VGG16, and VGG19, with and without Batch Normalization (BN),
             trained on ImageNet, available in pyTorch (v1.4).  
             Metrics fit by linear regression, RMSE reported.  }
    \label{fig:vgg-metrics}
\end{figure}
